Legacy Data Confounds Modern Genomics Studies

### 2018-08-09 legacy.tex
added figure 4 : Manhattan Plot

>>>>

\subsection{Combined Test}
To improve on the power of our test, we performed a test by combining the deviations from the null model for each SNP for each population.
Each population will have it's own deviation from the null for each position in the genome.
We computed the combined p value for each position by taking the sum of the deviations from each population and adjusting the degrees of freedom for the chi-squared test according to the number of populations with a segregating variant.
This resulted in an increase in the number of SNPs reaching genome wide significance to 3664. \ref{Manhattan}

\begin{figure*}
\includegraphics[width=\hsize,keepaspectratio]{ManhattanPlot.jpg}

\caption{Manhattan plot of the -log10 p values for the combined test using the deviations from each population of the 1kGP. 
There are 2007 and 3664 variants that reach p values greater than $ p < 10^{-8}$ and $ p < 10^{-6}$ respectively.
Crosses ( + ) represent SNPs that reach a genome wide significance greater than $ p < 10^{-6}$, the circles ( o ) are SNPs that reached values greater than 20, for clarity we implemented hard ceiling at 20.}
  \label{Manhattan}
\end{figure*}
